---
title: "Homework 8"
output: html_notebook
---

| Homework 8                     |                Data Analysis with R |
| :---                           |                                ---: |
| Due by 11:59 PM on Wed Oct 25  | Business Analytics Graduate Program |
| Submit via codePost            |                 BAIS:6060 Fall 2023 |

# Instructions

This homework covers Module 8. Refer to the corresponding materials and
ICE (with solutions) posted on ICON. Follow all of the instructions
given on prior homeworks, referring to them as necessary.

# Exercises

The included file `election_results.csv` contains county-by-county
U.S. presidential election results for 2016. Please review
`election_results_dictionary.txt` for full information. Note that there
is no data on Alaska, but Washington D.C. is included.



## #1

### (a)

Read the data into a data frame `df` with all default options for
`read_csv`. From this point forward in the homework, do not change the
contents of `df`.

```{r}

```

### (b)

Save all non-Iowa records in `df` into a new data frame `df_train` and
all Iowa records into `df_test`.

```{r}

```

### (c)

Train and test a `nearest_neighbor` classification model to predict
`republican`. Use `df_train` (excluding `region`, `state`, and `county`)
as the training data, and use `df_test` as the testing data.

In `my_metrics_nn`, save the output of `metrics(...)` for this model.
Also, save the elements of `df_test$county`, which are the counties that
are mispredicted by this model, in a new vector `mispredicted_nn`. Make
sure that `mispredicted_nn` is sorted in alphabetical order.

```{r}

```

### (d)

Repeat part (c) except for `logistic_reg`, saving the results in
`my_metrics_lr` and `mispredicted_lr`.

```{r}

```

# #2

Using `df` (excluding `region`, `state`, and `county`), do K-means
clustering of the entire data set with 2 centers. Noting that the output
of `kmeans` is a list, save the `centers` object in this list to a new
object called `my_centers`.

```{r}

```
